|

### 2024-12-04 02-methods.Rmd
edit: primary metrics

We focused on two primary metrics: (1) confidence in their answers, (2) perceived usefulness of interacting with the AI tutor, and (3) correctness of their answers (for task 3). Specifically,  students were asked, "How confident are you that the answer you provided is accurate?" on a five-point scale ranging from "not confident at all" to "very confident." They were also asked "How helpful was it to interact with the AI tutor?" This was also rated on a five-point scale, from "Not at all helpful" to "Very helpful." Finally, we also assessed the correctness of the response, whenever a correct answer was available (i.e., sound propogation questions).

>>>>

We focused on two primary metrics: (1) confidence in their answers, (2) perceived usefulness of interacting with the AI tutor. Specifically,  students were asked, "How confident are you that the answer you provided is accurate?" on a five-point scale ranging from "not confident at all" to "very confident." They were also asked "How helpful was it to interact with the AI tutor?" This was also rated on a five-point scale, from "Not at all helpful" to "Very helpful." Only for task 3, we had an additional metric which was the correctness of their answers.
